Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
revised 5.5

\subsection{Image Acquisition and Processing}
The current solution for imaging is solely based on the limited set of test images we were able to acquire, and is likely not robust enough for a full deployment. Once a successful deployment has been achieved, the image acquisition time needs to be fine-tuned so the license plate is always captured in the image. If the greedy cropping strategy for image processing is maintained, then it can be expanded upon to eliminate pieces on the left and right of the car in order to further reduce file size.

While contour mapping proved to be unsuccessful when processing the full images, further work should be done, once image acquisition has been fine-tuned, to crop the image and then apply contour mapping to the cropped image. The method failed originally because the license plate was not featured prominently in the image, and cropping the image more effectively could greatly help the contours of the license plate better stand out.

>>>>

\subsection{Image Acquisition and Processing}
The current solution for imaging is solely based on the limited set of test images we were able to acquire, and is likely not robust enough for a full deployment. Once a successful deployment has been achieved, the image acquisition time needs to be fine-tuned so the license plate is always captured in the image. If the naive cropping strategy for image processing is maintained, then it can be expanded upon to eliminate pieces on the left and right of the car in order to further reduce file size.

While contour mapping proved to be unsuccessful when processing the full images, further work should be done, once image acquisition has been fine-tuned, to crop the image and then apply contour mapping to the cropped image. The method failed originally because the license plate was not featured prominently in the image, and cropping the image more effectively could help the contours of the license plate better stand out.
